Topic modeling on EU and the USA research projects

### 2017-06-14 thesis_report/draft_thesis.tex
Related work: part (2/2)

>>>>

Griffiths and Steyvers describe LDA and present a Marckv Chain Monte Carlo
algorithm for inference in the model, illustrating the operation of the
suggested algorithm on a small dataset, and then on a larger corpus of PNAS
abstracts. Finally, they define the dynamics of the topics as a means of gaining
insight into the dynamics of science. As "hot" topics are identified the topics
that appear more frequently over the years (positive linear trend), and as
"cold" the ones that appear less frequently (negative linear trends over time).
We also analyze the topics over time, in order to highlight potential trends in
scientific research in EU and USA.

Inspired by Griffiths and Steyvers, L.Sun and Y.Yin wrote a paper, "Discovering
themes and trends in transportation research using topic modeling",
\cite{Sun201749} about topic modeling in transportation research. 
Considering approximately 17000 abstracts of articles published on 22 
leading journals in transportation research as documents, they infer 50 
topics by using LDA. Compared to "Finding scientific topics", Sun and 
Yin use more than one journal (22 popular journals) and they
investigate the journal-topic distribution and journal similarity. In our
analysis, we assume that EU and USA are 2 countries (like 2 different journals),
with different proportions of documents-projects, and we visualize the topic
similarity of the two countries per framework programme.

To best of our knowledge, there is no work done in the field of topic modeling
on scientific projects between EU and USA. There is limited information from
European Commission about the evolution and the results of the projects provided
by the official website.
